---
title: "bm2sel -- a selection of salmon runs based on illumina bodymap2 results in SRA"
author: "Vincent J. Carey, stvjc at channing.harvard.edu et al."
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{bm2sel -- selection from bodymap2 RNA-seq processed by salmon}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

```{r setup,echo=FALSE,results="hide"}
suppressPackageStartupMessages({
suppressMessages({
library(bm2sel)
library(BiocFileCache)
library(BiocStyle)
library(DT)
})
})
```

# Introduction

RNA-seq was applied to
16 tissues and results
contributed to NCBI SRA.
[Some background was reported at 
Ensembl](http://www.ensembl.info/2011/05/24/human-bodymap-2-0-data-from-illumina/).
This package is provided as an entry-level encounter
with a large project of recounting RNA-seq reads
carried out by Sean Davis of NCI.

# Surveying files with BiocFileCache

This vignette assumes local access to the salmon results
through execution of the `gatherForLocal` function
of this package (bm2sel).  The contents of the `destination` folder
used for that function
are then identified to the local `r Biocpkg("BiocFileCache")` through
code like
```
bfc = BiocFileCache()
fls <- dir(paste(getwd(), [destination], sep="/"), recursive=TRUE, full=TRUE)
res <- Map(bfcadd, rname=fls, fname=normalizePath(fls),
    MoreArgs=list(x=bfc, action = "asis"))
```

I used `compend` as the value of `destination`.
```{r lkca, cache=TRUE}
suppressPackageStartupMessages({
})
bfc = BiocFileCache()
#bfcquery(bfc, "compend")  # seems slow
```
To limit focus to files encoding information on the fragment-length
distribution:
```{r lkfld}
fldq = bfcquery(bfc, c("compend", "fld"))
fldq
```

# The sample-level data

This table was manually prepared by reviewing SRA
experiment pages.  The UBERON tags were manually added.

```{r lookmeta}
library(DT)
library(bm2sel)
data(bm2meta)
datatable(bm2meta)
```
 
# A view of fragment-length distributions

```{r fldlook}
fldpaths = fldq$fpath
fbins = sapply(fldpaths, getFld)
dists = apply(fbins, 2, function(x) rep(0:1000, x))
#dim(dists)
#qqnorm(dists[,1], type="l")
#for (i in 2:18) lines(qqnorm(dists[,i], plot=FALSE))
nns = strsplit(fldpaths, "/")
erx  = sapply(nns, "[", 7)
colnames(dists) = erx
opar = par(no.readonly=TRUE)
par(mar=c(9,3,3,3))
boxplot(data.frame(dists+1), log="y",
  ylab="fragment length", las=2)
par(opar)
```

